Urban Heat Risk Mapping Using Multiple Point Patterns in Houston, Texas

### 2016-11-16 reviewer_response.tex

Valid point. We rearranged the paper to put all of the information relevant to the algorithm in 2.4 together in the same section, making it easier to find details about how the model was fit. We also provided additional description to clarify what was meant by our comments such as ``the posterior is fully known.''

\subsection{I don't think the comments on convergence are adequate.   On page 13 line 10; how does MCSE alone provide evidence of convergence?   I think more is needed.}
We have attached traceplots to this document and can include them in the supplementary materials for the paper if desired. Additionally, we added further detail about how MCSE provides evidence of convergence on page 14 with the following statement:

\begin{displayquote}
In order to assess convergence, we examined traceplots for each of the parameters and used Monte Carlo standard error (MCSE). Jones et. al. (2006) calculate MCSE by dividing the chains into batches and using each batch mean to calculate variance between batches. Small MCSE values occur only when the variance between batches is low (i.e., each batch is approximately equal), thereby providing evidence of convergence.
\end{displayquote}

\subsection{I wasn't sure about claiming IG(2,1) or the Dirichlet prior were non-informative.   Using population counts sounds very informative (or was it the expected values that were used).}

In response to this comment we added a significant amount of justification in Section 2.3 detailing exactly why these priors are non-informative. Additionally, we clarified our comments in order to avoid the miscommunication that we were using population counts in our prior. The population counts only come into play through the data in the likelihood.

\subsection{It would be useful to understand some of the covariate posterior information; does the 0.51 versus 0.49 for males versus females section 3.3) really mean anything?   This might be a great parameter to set out the trace plots and density plots which would help provide information on convergence as well as understanding the relevance of what sounds like a modest difference to me.}

\textcolor{red}{For this, they ask for trace plots and density plots, but I'm not sure how that answers the question he asks. I've included the posterior delta densities, so that if desired you can mentally multiply that image by the proportions to ballpark how many people that difference might represent, but I could actually create a figure of the distribution of the counts and include it in the text if you think it's a good idea.}

\subsection{Why do a spatial misalignment (Brunsdon and Comber)?   There are comparable numbers of census tracts and grid squares; using census tracts directly sounds like a tractable GIS problem (the denominator is the area of the census tract, points-in-polygons can count the necessary points).   I couldn't see anything in the mathematics of the intensity that would prevent the census tracts being used, and you remove a layer of approximation.}

We responded to this comment by adding the following text to the article:

\begin{displayquote}
A potential solution to avoid realigning the census data to the grid cells is to let the census block groups equal the $\mathcal{G}_k$ denoted in \eqref{lambda} rather than the grid cells. However, the heat information used in this research (described in detail in Section \ref{sec:temp_data}) is provided at a 1-km$^2$ resolution and these grid cells were chosen to align exactly with the available heat data. Using the block groups in place of the grid cells would necessitate aligning the heat information to the census block group areas. Because heat is our primary variable of interest we prefer realigning the demographic information to the grid associated with the heat data as opposed to the alternative. Therefore, we proceed having aligned the population data as described.
\end{displayquote}

\subsection{Heat enters as an upper level covariate, with ecological fallacy risks?   Are the census data not available to study how tsome of these features vary with key other demographics?   I appreciate all the census data are disclosure limited but some multiway information on air conditining and age band could really limit the potential problems with confounders in the aggregate analysis.}

In order to address this concern, we examined the impact of additional demographic covariates from the census data on our model. We also included all two-way interaction terms between the various covariates as potential predictors in our model in order to mitigate the potential problems with confounders (see Table X), as suggested by the reviewer.

\subsection{Although you make a comment in the end about the lack of suitable model fit diagnostics there is a lot more that is already available.   WAIC / Gneiting and Tillmans's proper scoring rules seem appropriate given a major outcome is a risk map.}

The comment in our article was not about model fit diagnostics that allow you to compare different models, but rather about diagnostics that are an objective measure of how well the chosen model fits the data. Neither Tillman Gneiting's proper scoring rules or WAIC provide a solution to this particular problem. \textcolor{red}{Can you add a discussion of the proper scoring rules here?} Additionally, Gelman et. al. (2014; \textit{Statistics and Computing} argue that ``a cost of using WAIC is that it relies on a partition of the data into n pieces, which is not so easy to do in some structured-data settings such as time series, spatial, and network data'' and suggest that this makes WAIC an inappropriate measure for the type of spatial model we use in this paper. However, following the work of Leininger, we did implement some simple posterior predictive checks in order to show that our analysis is generally congruent with the observed data.

\subsection{From an applications point of view I'd really like to see the counts (posterior predictive density) as well as the probabilities in figure 4.}

\textcolor{red}{I've added in the delta posterior densities, giving an idea of the counts in general, but should I go ahead and add the counts for the ages specifically as well?}

\section{Response to Comments from Reviewer 2}
\subsection{The authors need to explain explicitly how to combine/connect and use data information from 2 different periods of time (heat-related emergency calls  during 2006-2010 vs. mortality data between 1999 and 2006).}

\textcolor{red}{Via email, you suggested that we show that the demographic makeup of Houston didn't change much over the window that we consider. Do you have any idea how to show that? Should I examine census data over that period? What do we do in the case where there was a major demographic shift?}

\subsection{The prior assumptions and choices need to be justified especially for those non-informative and vague priors. Also, "Because the priors for $\alpha_p, \gamma_p$" etc., "are all conjugate, their posterior distributions are known..." is not clear to me that the claim is valid. It would also be helpful if the results from the MCMC are presented so to confirm convergence.}

We added additional detail justifying our prior assumptions and also explicitly demonstrated the conjugacy of the Dirichlet prior. Because we have so many parameters, we prefer not to include trace plots in the paper, but we have attached them to this document and can add them in the supplementary materials for the paper if desired.

\subsection{The labels of colours in figures 2 and 3 are hard to see and the 95\%CI in figure 3 is not clear.}

We have improved the visibility of the labels, and made the widths of the 95\% confidence intervals more obvious.

### 2016-11-26 jrssc-mpp.tex
Formatted reviewer response sheet. Added DIC values for those MCMC runs that have finished, further clarified the algorithm used to fit the model.

\usepackage[letterpaper]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage{dsfont}
\usepackage{bm}
\usepackage{multirow}

@@

The vector $\boldsymbol\mu$ is of particular interest in our model because it represents
the combination of information from many different sources of health data into
a single measure of the overall relative risk of heat on 
health rather than just the impact of heat on one indicator. In spite of a common mean, 
in \eqref{phiprior} we allow a separate variance parameter for each health outcome 
($\sigma^2_p$). We make this assumption primarily from the kernel density estimates 
in Figure \ref{kde} which 
show that the density of the 911 calls is more peaked (i.e. larger variance of density values).

An implicit assumption with \eqref{phiprior} is the independence assumption among the log relative risks for each health outcome given the overall, ``cumulative'' log relative risk surface $\boldsymbol{\mu}$. For the application considered here this assumption is likely to, approximately, hold because the time frame for the 911 call data is 2006-2010 while the time frame for the mortality data is 1999-2006 (a minimal overlap); however, in other applications independence may not hold. In such cases, a multivariate spatial model (see \cite{Genton2015} for a discussion) could be used in place of \eqref{phiprior}. We note the possible benefit of modeling dependence between the log relative risks but we do not explore this option here.

@@

\subsection{Hyperprior Layer}
\textcolor{red}{At the hyperior prior layer of the model, we outline our prior assumptions for the model
parameters in Sections \ref{likelayer} and \ref{process}. Because $\boldsymbol{\alpha}_p = 
(\alpha_p(0),\dots,\alpha_p(113))'$ are probabilities where $\sum_a \alpha_p(a) = 1$, 
we assume $$\boldsymbol{\alpha}_{p} \sim \text{Dir}(\mathbf{1}_{113})$$ for all $p$ where 
$\text{Dir}(\cdot)$ denotes the Dirichlet distribution and $\mathbf{1}_{113}$ is a $1\times 113$ vector of ones. Note that for a symmetric Dirichlet distribution with a concentration parameter of 1 across $M$ categories, its density function simplifies to 
\begin{equation}
\frac{1}{C}\prod_{i=1}^M x_i^{1 - 1} = \frac{1}{C},
\end{equation}
where $C$ is a constant. Therefore, assuming $\boldsymbol\alpha_p \sim \text{Dir}(\mathbf{1}_{113})$ is equivalent to applying a uniform prior to $\boldsymbol\alpha_p$, and it follows that it is non-informative. Further, if we let $f(\boldsymbol\alpha_p)$ and $f(\boldsymbol\alpha_p \mid \mathbf{Z}_p)$ represent the prior and posterior distributions for $\alpha_p$, respectively, and let $n_{p,a}$ be the number of people who experienced health outcome $p$ at age $a$, then we can use the likelihood in \eqref{likelihood} to show that the Dirichlet prior described for $\boldsymbol{\alpha}_p$ is conjugate:  
\begin{align}
f(\boldsymbol{\alpha}_p \mid \mathbf{Z}_p) &\propto \text{f}(\boldsymbol{\alpha}_p)f(\mathbf{Z}_p \mid \boldsymbol\Theta) \notag \\
&\propto \left[\prod_{a=0}^{113}\left(\alpha_p(a)\right)^{1-1}\right]\left[\prod_{a=0}^{113} \left(\alpha_p(a)\right)^{n_{p,a}}\right]  \label{apost} \\
&= \prod_{a=0}^{113} \left(\alpha_p(a)\right)^{(n_{p,a}+1)-1}. \notag
\end{align} 
Stated explicitly, the posterior distribution of $\boldsymbol\alpha_p$ is a Dirichlet distribution with concentration parameters $(n_{p,0} + 1, n_{p,1} + 1, \dots, n_{p,113}+1)$.
In a similar vein, we assume $$\boldsymbol\gamma_p = (\gamma_p(\text{female}), \gamma_p(\text{male}))' \sim \text{Dir}(\mathbf{1}_2)$$ and $$\boldsymbol\xi_p = (\xi_p(\text{Asian}), \dots, \xi_p(\text{White}))' \sim \text{Dir}(\mathbf{1}_4),$$ which, by the same argument, are also non-informative and conjugate priors.}

@@

\subsection{Model Fitting}
\textcolor{red}{We fit this model within a Bayesian framework. For each health outcome $p = 1, \dots, P$, randomly generate draws for $\delta_p$ from the known posterior, $\mathcal{G}(n_p + 0.001, 1.001)$. Similarly, because the priors
for $\boldsymbol{\alpha}_p$, $\boldsymbol{\gamma}_p$, and $\boldsymbol{\xi}_p$ are all conjugate, their posterior
distributions are known and can be drawn from directly. That is, for $p = 1, \dots, P$ we can easily obtain random draws from $\text{Dir}(n_{p,0} + 1, n_{p,1} + 1, \dots, n_{p,113})$, $\text{Dir}(n_{p,Female} + 1, n_{p,Male} + 1)$, and $\text{Dir}(n_{p,Asian} + 1, \dots, n_{p,White} + 1)$, where as before $n_{p,0}$ denotes the number of people who experienced health outcome $p$ at age $0$, $n_{p,Female}$ indicates the number of females who experienced health outcome $p$, and so on.}

 \textcolor{red}{The posterior densities for the rest of the parameters are unknown and so we obtain draws from the posterior using a Metropolis within Gibbs sampler of the following form:
\begin{enumerate}
  \item \label{draws2} For $p = 1, \dots, P$, sample $\sigma^2_p \sim \left[ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p\right]$;
  \item \label{drawphi} For $p = 1, \dots, P$, sample $\boldsymbol\phi^\star_p \sim \left[ \boldsymbol\phi^\star_p | \sigma^2_p, \mathbf{M}_p \right]$;
  \item \label{drawsmu} Sample $\sigma^2_\mu \sim \left[ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, \mathbf{M}_\mu \right]$;
  \item \label{drawmu} Sample $\boldsymbol{\mu} \sim \left[ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} \right]$; and
  \item \label{drawbeta} Sample $\boldsymbol{\beta} \sim \left[ \boldsymbol{\beta} | \boldsymbol{\mu}, \sigma^2_\mu, \mathbf{M}_\mu \right]$.
\end{enumerate}}

\textcolor{red}{
We use the notation $\left[\theta | \psi_1, \dots, \psi_k \right]$ to represent the complete conditional for the parameter $\theta$ dependent on parameters $\psi_1, \dots, \psi_k$. Note that for steps \ref{draws2}, \ref{drawsmu}, and \ref{drawbeta} the complete conditional distributions are}
\begin{equation}
\sigma^2_p \sim \mathcal{IG}\left(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}\boldsymbol\phi_p^{\star\prime}\mathbf{M}_p^{-1}\boldsymbol\phi_p^\star\right),
\end{equation}
\begin{equation}
\sigma^2_\mu \sim \mathcal{IG}\left(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)^\prime\mathbf{M}^{-1}_\mu(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)\right), \text{ and }
\end{equation}
\begin{equation}
\boldsymbol{\beta} \sim \mathcal{N}\left(\sigma_\mu^{-2}\Sigma^{\star}\mathbf{X}^\prime\mathbf{M}_\mu^{-1}\boldsymbol\mu, \Sigma^\star)\right), 
\end{equation}
where $M_p$ and $M_\mu$ are defined as in \eqref{phiprior} and \eqref{mu} and where $\Sigma^\star = \left[\frac{1}{50}I_Q + \frac{1}{\sigma^2_\mu}\mathbf{X}^\prime \mathbf{M}_\mu^{-1}\mathbf{X}\right]^{-1}$. 
\textcolor{red}{
Because these belong to known families they can be drawn from directly using a Gibbs update, but the complete conditional distributions in steps \ref{drawphi} and \ref{drawmu} are not known and require a Metropolis-Hastings (MH) update. Using a sampler of this design, 10000 draws were taken from the posterior distributions for each of these parameters, after a burn-in of 10000.\footnote{R code used to implement this algorithm is provided in the supplementary materials.m} In order to assess convergence, we examined traceplots for each of the parameters and used Monte Carlo standard error (MCSE). \cite{Jones2006} calculate MCSE by dividing the chains into batches and using each batch mean to calculate variance between batches. Small MCSE values occur only when the variance between batches is low (i.e., each batch is approximately equal), thereby providing evidence of convergence. We calculated MCSE using the \texttt{mcmcse} package in R \citep{Flegal2015}, and the largest MCSE value for all of our parameters was XXXXX. Based on these MCSE values and visual inspection of the traceplots, we are satisfied that convergence was attained.}

@@

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Tue, Nov 03, 2015 - 15:11:28
\begin{table}
  \caption{DIC values for models fit with different temperature measurements.} 
  \label{DIC} 
\begin{tabular}{@{\extracolsep{5pt}} cc} 
\\[-1.8ex]\hline
\hline \\[-1.8ex]  
Temperature Measurement & DIC \\
\hline \\[-1.8ex]  
HI Max & $220991$ \\ 
HI Min & $221016$ \\ 
T2 Max & $220998$ \\ 
T2 Min & $220999$ \\ 
SWBG Max & $221008$ \\ 
SWBG Min & $221021$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

  \begin{tabular}{@{\extracolsep{5pt}} lccccccccc|c}
  \\[-1.8ex]\hline
  \hline \\[-1.8ex]
  & \multicolumn{9}{c}{Variables} & \\
  & \rot{\% over 65} & \rot{\% under 5} & \rot{\% Black} & \rot{\% Hispanic} & \rot{\% w/o AC} & \rot{\% disabled} & \rot{\% living alone} & \rot{\% in poverty} & \rot{Interactions} & DIC \\\hline
  Model 01 &   &   &   &   &   &   &   &   &   & 12345 \\
  Model 02 & X & X &   &   &   &   &   &   &   & 12345 \\
  Model 03 &   &   & X & X &   &   &   &   &   & 12345 \\
  Model 04 &   &   &   &   & X & X & X & X &   & 12345 \\
  Model 05 & X & X & X & X &   &   &   &   &   & 12345 \\
  Model 06 & X & X &   &   & X & X & X & X &   & 12345 \\
  Model 07 &   &   & X & X & X & X & X & X &   & 12345 \\
  Model 08 & X & X & X & X & X & X & X & X &   & 12345 \\
  Model 09 & X & X &   &   &   &   &   &   & X & 12345 \\
  Model 10 &   &   & X & X &   &   &   &   & X & 12345 \\
  Model 11 &   &   &   &   & X & X & X & X & X & 12345 \\
  Model 12 & X & X & X & X &   &   &   &   & X & 12345 \\
  Model 13 & X & X &   &   & X & X & X & X & X & 12345 \\
  Model 14 &   &   & X & X & X & X & X & X & X & 12345 \\
  Model 15 & X & X & X & X & X & X & X & X & X & 12345 \\
  \hline\\[-1.8ex]
  \end{tabular}

@@

\begin{figure}
  \centering
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_911.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_mortality.pdf}
  \end{minipage}
  \caption{Posterior density plots for $\delta_{911}$ and $\delta_{Mort}$.}
  \label{fig:delta_kde}
\end{figure}

>>>>

\usepackage[letterpaper]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage{dsfont}
\usepackage{bm}
\usepackage{multirow}
\usepackage[linesnumbered,lined,ruled]{algorithm2e}

@@

The vector $\boldsymbol\mu$ is of particular interest in our model because it represents
the combination of information from many different sources of health data into
a single measure of the overall relative risk of heat on 
health rather than just the impact of heat on one indicator. In spite of a common mean, 
in \eqref{phiprior} we allow a separate variance parameter for each health outcome 
($\sigma^2_p$). We make this decisions based primarily on the kernel density estimates 
in Figure \ref{kde} which 
show that the density of the 911 calls is more peaked (i.e. larger variance of density values).

\textcolor{red}{The primary assumption we make in \eqref{phiprior} is that the relative risk surfaces for each health outcome share a common, underlying risk surface that is constant with respect to time. Naturally, the assumption would be violated if there is temporal variability between the relative risk surface in 1999-2006 (the time window for the mortality data) and 2006-2010 (the time window for the 911 call data). Unfortunately, given the data available to us, our assumption of a time-invariant relative risk surface is not able to be evaluated. That is, we would need information on the relative risk of mortality between 2006-2010 to investigate any inherent differences in the surface between 1999-2006 and 2006-2010 (which we don't have). Likewise, we would need 911 call data for the years 1999-2006 to assess any temporal differences in the risk of a 911 call (which we also don't have). While the possibility of a time-varying risk surface would be interesting from an epidemiological perspective, we leave this for future work.}

\textcolor{red}{An additional implicit assumption with \eqref{phiprior} is the independence assumption among the log relative risks for each health outcome given the overall, ``cumulative'' log relative risk surface $\boldsymbol{\mu}$. For the application considered here this assumption is likely to, approximately, hold because the time frame for the 911 call data is 2006-2010 while the time frame for the mortality data is 1999-2006 (a minimal overlap); however, in other applications independence may not hold. In such cases, a multivariate spatial model (see \cite{Genton2015} for a discussion) could be used in place of \eqref{phiprior}. We note the possible benefit of modeling dependence between the log relative risks but we do not explore this option here.}

@@

\subsection{Hyperprior Layer}\label{sec:hyperprior}
\textcolor{red}{At the hyperior prior layer of the model, we outline our prior assumptions for the model
parameters in Sections \ref{likelayer} and \ref{process}. Because $\boldsymbol{\alpha}_p = 
(\alpha_p(0),\dots,\alpha_p(113))'$ are probabilities where $\sum_a \alpha_p(a) = 1$, 
we assume $$\boldsymbol{\alpha}_{p} \sim \text{Dir}(\mathbf{1}_{113})$$ for all $p$ where 
$\text{Dir}(\cdot)$ denotes the Dirichlet distribution and $\mathbf{1}_{113}$ is a $1\times 113$ vector of ones. Note that for a symmetric Dirichlet distribution with a concentration parameter of 1 across $M$ categories, its density function simplifies to 
\begin{equation}
\frac{1}{C}\prod_{i=1}^M x_i^{1 - 1} = \frac{1}{C},
\end{equation}
where $C$ is a constant. Therefore, assuming $\boldsymbol\alpha_p \sim \text{Dir}(\mathbf{1}_{113})$ is equivalent to applying a uniform prior to $\boldsymbol\alpha_p$, and it follows that it is non-informative. Further, if we let $f(\boldsymbol\alpha_p)$ and $f(\boldsymbol\alpha_p \mid \mathbf{Z}_p)$ represent the prior and posterior distributions for $\alpha_p$, respectively, and let $n_{p,a}$ be the number of people who experienced health outcome $p$ at age $a$, then we can use the likelihood in \eqref{likelihood} to show that the Dirichlet prior described for $\boldsymbol{\alpha}_p$ is conjugate:  
\begin{align}
f(\boldsymbol{\alpha}_p \mid \mathbf{Z}_p) &\propto \text{f}(\boldsymbol{\alpha}_p)f(\mathbf{Z}_p \mid \boldsymbol\Theta) \notag \\
&\propto \left[\prod_{a=0}^{113}\left(\alpha_p(a)\right)^{1-1}\right]\left[\prod_{a=0}^{113} \left(\alpha_p(a)\right)^{n_{p,a}}\right]  \label{apost} \\
&= \prod_{a=0}^{113} \left(\alpha_p(a)\right)^{(n_{p,a}+1)-1}. \notag
\end{align} 
Stated explicitly, the posterior distribution of $\boldsymbol\alpha_p$ is a Dirichlet distribution with concentration parameters $(n_{p,0} + 1, n_{p,1} + 1, \dots, n_{p,113}+1)$.
In a similar vein, we assume $$\boldsymbol\gamma_p = (\gamma_p(\text{female}), \gamma_p(\text{male}))' \sim \text{Dir}(\mathbf{1}_2)$$ and $$\boldsymbol\xi_p = (\xi_p(\text{Asian}), \dots, \xi_p(\text{White}))' \sim \text{Dir}(\mathbf{1}_4),$$ which, by the same argument, are also non-informative and conjugate priors.}

@@

\subsection{Model Fitting}
\begin{algorithm}
  Let $N$ be the number of MCMC draws, large enough that convergence is attained.
  \BlankLine
  \For{$p$ in $1:P$}{
  Sample $N$ draws from $\delta_{p} \sim \mathcal{G}(n_p + 0.001, 1.001)$\;
  Sample $N$ draws from $\boldsymbol\alpha_p \sim \text{Dir}\left(n_{p,0}+1, n_{p,1}+1, \dots, n_{p,113} + 1\right)$\;
  Sample $N$ draws from $\boldsymbol\gamma_p \sim \text{Dir}\left(n_{p,\text{Female}} + 1, n_{p,\text{Male}} + 1\right)$\;
  Sample $N$ draws from $\boldsymbol\xi_p \sim \text{Dir}\left(n_{p,\text{Asian}} + 1, \dots, n_{p,\text{White}}\right)$\;
  }
  \For{$i$ in $1:N$}{
    \For{$p$ in $1:P$} {
      Sample $\sigma^2_p \sim \left[ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p\right]$\label{draws2}\;
      Sample $\boldsymbol\phi^\star_p \sim \left[ \boldsymbol\phi^\star_p | \sigma^2_p, \mathbf{M}_p \right]$\label{drawphi}\;
    }
    Sample $\sigma^2_\mu \sim \left[ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, \mathbf{M}_\mu \right]$\label{drawsmu}\;
    Sample $\boldsymbol{\mu} \sim \left[ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} \right]$\label{drawmu}\;
    Sample $\boldsymbol{\beta} \sim \left[ \boldsymbol{\beta} | \boldsymbol{\mu}, \sigma^2_\mu, \mathbf{M}_\mu \right]$\label{drawbeta}\;
  }
  \caption{Model fitting algorithm. \label{algo:model_fit}}

\end{algorithm}
\textcolor{red}{We fit this model within a Bayesian framework, using the Markov Chain Monte Carlo (MCMC) algorithm outlined in Algorithm \ref{algo:model_fit}. Notice that because the parameters on lines 2-7 all have conjugate priors (as described in Section \ref{sec:hyperprior}), their posterior densities are completely known and all $N$ draws can be taken simultaneously. Recall that $n_{p,0}$ denotes the number of people who experienced health outcome $p$ at age $0$, $n_{p,Female}$ indicates the number of females who experienced health outcome $p$, and so on. }

 \textcolor{red}{The complete posterior densities for the remaining parameters are unknown and so we obtain draws from the posterior using the Metropolis within Gibbs sampler outlined on lines 8-16 of Algorithm \ref{algo:model_fit}. We use the notation $\left[\theta | \psi_1, \dots, \psi_k \right]$ to represent the complete conditional for the parameter $\theta$ dependent on parameters $\psi_1, \dots, \psi_k$. Note that for the parameter updates on lines \ref{draws2}, \ref{drawsmu}, and \ref{drawbeta} the complete conditional distributions are}
\begin{equation}
\sigma^2_p \sim \mathcal{IG}\left(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}\boldsymbol\phi_p^{\star\prime}\mathbf{M}_p^{-1}\boldsymbol\phi_p^\star\right),
\end{equation}
\begin{equation}
\sigma^2_\mu \sim \mathcal{IG}\left(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)^\prime\mathbf{M}^{-1}_\mu(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)\right), \text{ and }
\end{equation}
\begin{equation}
\boldsymbol{\beta} \sim \mathcal{N}\left(\sigma_\mu^{-2}\Sigma^{\star}\mathbf{X}^\prime\mathbf{M}_\mu^{-1}\boldsymbol\mu, \Sigma^\star)\right), 
\end{equation}
where $M_p$ and $M_\mu$ are defined as in \eqref{phiprior} and \eqref{mu} and where $\Sigma^\star = \left[\frac{1}{50}I_Q + \frac{1}{\sigma^2_\mu}\mathbf{X}^\prime \mathbf{M}_\mu^{-1}\mathbf{X}\right]^{-1}$. 
\textcolor{red}{
Because these belong to known families they can be drawn from directly using a Gibbs update, but the complete conditional distributions in steps \ref{drawphi} and \ref{drawmu} are not known and require a Metropolis-Hastings (MH) update.}

\textcolor{red}{Using a sampler of this design, 10000 draws were taken from the posterior distributions for each of these parameters, after a burn-in of 10000.\footnote{R code used to implement this algorithm is provided in the supplementary materials.} In order to assess convergence, we examined traceplots for each of the parameters and used Monte Carlo standard error (MCSE). \cite{Jones2006} calculate MCSE by dividing the chains into batches and using each batch mean to calculate variance between batches. Small MCSE values occur only when the variance between batches is low (i.e., each batch is approximately equal), thereby providing evidence of convergence. We calculated MCSE using the \texttt{mcmcse} package in R \citep{Flegal2015}, and the largest MCSE value for all of our parameters was XXXXX. Based on these MCSE values and visual inspection of the traceplots, we are satisfied that convergence was attained.}

@@

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Tue, Nov 03, 2015 - 15:11:28
\begin{table}
  \caption{DIC values for models fit with different temperature measurements.} 
  \label{DIC} 
\begin{tabular}{@{\extracolsep{5pt}} cc} 
\\[-1.8ex]\hline
\hline \\[-1.8ex]  
Temperature Measurement & DIC \\
\hline \\[-1.8ex]  
HI Max & $220474$ \\ 
HI Min & $221016$ \\ 
T2 Max & $220998$ \\ 
T2 Min & $220999$ \\ 
SWBG Max & $221008$ \\ 
SWBG Min & $221021$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

  \begin{tabular}{@{\extracolsep{5pt}} lccccccccc|c}
  \\[-1.8ex]\hline
  \hline \\[-1.8ex]
  & \multicolumn{9}{c}{Variables} & \\
  & \rot{\% over 65} & \rot{\% under 5} & \rot{\% Black} & \rot{\% Hispanic} & \rot{\% w/o AC} & \rot{\% disabled} & \rot{\% living alone} & \rot{\% in poverty} & \rot{Interactions} & DIC \\\hline
  Model 01 &   &   &   &   &   &   &   &   &   & 12345 \\
  Model 02 & X & X &   &   &   &   &   &   &   & 12345 \\
  Model 03 &   &   & X & X &   &   &   &   &   & 220523 \\
  Model 04 &   &   &   &   & X & X & X & X &   & 220482 \\
  Model 05 & X & X & X & X &   &   &   &   &   & 220526 \\
  Model 06 & X & X &   &   & X & X & X & X &   & 220512 \\
  Model 07 &   &   & X & X & X & X & X & X &   & 220497 \\
  Model 08 & X & X & X & X & X & X & X & X &   & 220498 \\
  Model 09 & X & X &   &   &   &   &   &   & X & 220529 \\
  Model 10 &   &   & X & X &   &   &   &   & X & 220455 \\
  Model 11 &   &   &   &   & X & X & X & X & X & 220493 \\
  Model 12 & X & X & X & X &   &   &   &   & X & 220522 \\
  Model 13 & X & X &   &   & X & X & X & X & X & 12345 \\
  Model 14 &   &   & X & X & X & X & X & X & X & 12345 \\
  Model 15 & X & X & X & X & X & X & X & X & X & 12345 \\
  \hline\\[-1.8ex]
  \end{tabular}

@@

\begin{figure}
  \centering
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_911.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{./imgs/delta_mortality.pdf}
  \end{minipage}
  \caption{Posterior density plots for $\delta_{911}$ and $\delta_{\text{Mort}}$. The posterior mean for $\delta_{911}$ is 1387 and the posterior mean for $\delta_{\text{Mort}}$ is 15228}
  \label{fig:delta_kde}
\end{figure}
